# Sample reports

---
output:
  html_document:
   highlight: tango
---

```{r load-packages, include=FALSE}
library(data.table)
library(jsonlite)

```



```{r, include=FALSE}
config_json = as.data.table(fromJSON(snakemake@params$config))

```
Overview report of workflow done for sample `r snakemake@params$sample_name `.




## Report files:
* [Main QC summary - (MultiQC)](`r basename(snakemake@input$multiqc)`)
* `r if(unique(config_json$qc_qualimap_DNA) == TRUE){paste0("[Detailed mapping QC - (Qualimap)](../../",snakemake@input$qc_qualimap_DNA,")")} `
* [Detailed raw fastq QC - (FastQC)](../../`r snakemake@input$raw_fastq_R1_report`)
* [Detailed raw fastq QC - (FastQC)](../../`r snakemake@input$raw_fastq_R2_report`)
* `r if(unique(config_json$qc_picard_RNA) == TRUE){paste0("[RNA-Seq metrics - Picard](../../",snakemake@input$qc_picard_RNA,")")} `
* `r if(unique(config_json$feature_count) == TRUE){paste0("[RNA-Seq metrics - featureCounts](../../",snakemake@input$feature_count,")")} `
* `r if(unique(config_json$fastq_screen) == TRUE){paste0("[RNA-Seq metrics - Fastq screen](../../",snakemake@input$fastq_screen,")")} `
* `r if(unique(config_json$biobloom) == TRUE){paste0("[RNA-Seq metrics - BioBloom Tools](../../",snakemake@input$biobloom,")")} `
* `r if(unique(config_json$qc_biotypes_RNA) == TRUE){paste0("[RNA-Seq metrics - Biotypes](../../",snakemake@input$qc_biotypes_RNA,")")} `

---

Return to [start page](../final_alignment_report.html)

---