---
# Final report
output:
  html_document:
    highlight: tango

---

```{r load-packages, include=FALSE}
library(data.table)
library(jsonlite)

```


```{r, include=FALSE}
config_json = as.data.table(fromJSON(snakemake@params$config))

```
## Main report:
`r paste0("* [Multi-sample main QC summary (MultiQC)](../",snakemake@input$all_sample_multiqc,")  \\")`
`r if(unique(config_json$cross_sample_correlation)   == TRUE){paste0("* [ Cross sample correlation report](../",snakemake@input$cross_sample_correlation,  ")  \\")}`
`r if(unique(config_json$qc_fastq_screen_RNA)   == TRUE){paste0("[* Fastq screen RNA QC report](../",snakemake@input$qc_fastq_screen_RNA,  ")  \\")} `
`r if(unique(config_json$feature_count)   == TRUE){paste0("* [Feature count report](../",snakemake@input$feature_count,  ")  \\")} `
`r if(unique(config_json$qc_dupradar_RNA)   == TRUE){paste0("* [All samples RNA-Seq metrics - Dupradar duprateExpBoxplot](../",snakemake@input$dupraxpbox,  ")  \\")} `
`r if(unique(config_json$qc_dupradar_RNA)   == TRUE){paste0("* [All samples RNA-Seq metrics - Dupradar expressionHist](../",snakemake@input$exphist,  ")  \\")} `
`r if(unique(config_json$qc_dupradar_RNA)   == TRUE){paste0("* [All samples RNA-Seq metrics - Dupradar duprateExpDens](../",snakemake@input$dupraexpden,  ")  \\")} `
`r if(unique(config_json$qc_dupradar_RNA)   == TRUE){paste0("* [All samples RNA-Seq metrics - Dupradar multimapPerGene](../",snakemake@input$multipergene,  ")  \\")} `
`r if(unique(config_json$qc_dupradar_RNA)   == TRUE){paste0("* [All samples RNA-Seq metrics - Dupradar readDist](../",snakemake@input$readdist,  ")  \\")} `
----------------------------------------------------------

## Individual samples reports:
```{r, results='asis', echo=FALSE}
for (i in snakemake@params$sample_name){
   cat('\n')
   #cat(paste0(" * [Sample ", i, " report](",i,".final_sample_report.html)\n"))
   cat(paste0(" * [Sample ", i, " report](./",i,"/single_sample_alignment_report.html)\n"))
   cat('\n')
}
```





---


