---
title:  Sample reports DNA
output:
  html_document:
    highlight: tango
    toc: true
    toc_depth: 2
    toc_float: 
      collapsed: no
      smooth_scroll: yes
---

```{r load-packages, include=FALSE}
library(data.table)
library(jsonlite)

```

```{r, results='asis', echo=FALSE}
# BASEDIR <- "/mnt/ssd/"
# STAGE <- "210604"
# PROJECT <- "alignment_qc_71"
# WORKDIR <- paste0(BASEDIR,STAGE,"_",PROJECT)
# INPUTFILES <- paste0(WORKDIR,"/")
BASEDIR <- "/mnt/ssd/ssd_1/workspace/katka/Rmarkdown/"
STAGE <- "201111"
PROJECT <- "TP53-20201111"
WORKDIR <- paste0(BASEDIR,STAGE,"_",PROJECT)
INPUTFILES <- paste0(WORKDIR,"/")

```


```{r, include=FALSE}
config_json = as.data.table(fromJSON(paste0(INPUTFILES,"config.json")))
```
`r if(unique(config_json$qc_picard_DNA)   == TRUE){"## QC picard DNA reports"}`
`r if(unique(config_json$qc_picard_DNA)   == TRUE){paste0("[",snakemake@input$picard,  "](./",snakemake@input$picard,  ")")} `

`r if(unique(config_json$qc_qualimap_DNA) == TRUE){"## QC qualimap DNA reports"}`
`r if(unique(config_json$qc_qualimap_DNA) == TRUE){paste0("[",snakemake@input$qualimap,"](./",snakemake@input$qualimap,")")} `

`r if(unique(config_json$qc_samtools_DNA) == TRUE){"## QC samtools DNA reports"}`
`r if(unique(config_json$qc_samtools_DNA) == TRUE){paste0("[",snakemake@input$samtools,"](./",snakemake@input$samtools,")")} `


# The end















